### 2024-05-06 Tables/MD_noMD_uncompCMI_synth.tex
Updates from Overleaf
fix sample of nonprofits and add synthetic difference in differences graphs

\caption{\label{tab:MD_noMD_uncompCMI_synth}Non-MD vs. MD Executive Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Uncompensated Care} & \multicolumn{1}{c}{Case Mix Index} \\
 & (1) & (2)\\
\midrule
NP w/out MD Exec x Post Programs & 0.02$^{*}$ & 0.03$^{***}$\\
 & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  & \\
NP w/ MD Exec & $\checkmark$ & $\checkmark$\\
 &  & \\
\addlinespace
Observations & 15,585 & 2,900\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome}\\
\multicolumn{3}{l}{variables.}\\
\multicolumn{3}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{3}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{3}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_uncompCMI_synth}Non-MD vs. MD Executive Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Uncompensated Care} & \multicolumn{1}{c}{Case Mix Index} \\
 & (1) & (2)\\
\midrule
NFP w/out MD Exec x Post Programs & 0.02$^{*}$ & 0.03$^{**}$\\
 & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  & \\
NFP w/ MD Exec & $\checkmark$ & $\checkmark$\\
 &  & \\
\addlinespace
Observations & 15,610 & 2,900\\
\bottomrule
\multicolumn{3}{l}{\textsuperscript{} Results from Equation with uncompensated care and CMI as outcome variables.}\\
\multicolumn{3}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{3}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{3}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}

### 2024-05-06 Tables/forprofit_readmort_synth.tex
fix sample of nonprofits and add synthetic difference in differences graphs

\caption{\label{tab:forprofit_readmort_synth}Comparison to For-Profit Readmission and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Weighted Avg. Readmission Rate} & \multicolumn{3}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For-Profit x Post Programs & -0.07 & -0.32$^{**}$ & -0.03 & -0.01 & -0.17 & 0.02\\
 & (0.04) & (0.11) & (0.06) & (0.04) & (0.11) & (0.06)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 15,585 & 2,900 & 4,705 & 15,505 & 2,895 & 4,690\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_readmort_synth}Comparison to For-Profit Readmission and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Weighted Avg. Readmission Rate} & \multicolumn{3}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Programs & -0.07 & -0.32$^{**}$ & -0.03 & -0.01 & -0.17 & 0.02\\
 & (0.04) & (0.11) & (0.06) & (0.04) & (0.11) & (0.06)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
In-Sample NFPs & $\checkmark$ &  &  & $\checkmark$ &  & \\
NFPs w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
NFPs w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 15,610 & 2,900 & 4,705 & 15,530 & 2,895 & 4,690\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-05-06 Tables/forprofit_uncompCMI_synth.tex
fix sample of nonprofits and add synthetic difference in differences graphs

\caption{\label{tab:forprofit_uncompCMI_synth}Comparison to For-Profit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Uncompensated Care} & \multicolumn{3}{c}{Case Mix Index} \\
 & (1) & (2) & (3) & (1) & (2) & (3)\\
\midrule
For-Profit x Post Programs & 0.06$^{***}$ & 0.08$^{***}$ & 0.06$^{***}$ & 0 & 0.02$^{**}$ & 0\\
 & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
All Nonprofits & $\checkmark$ &  &  & $\checkmark$ &  & \\
Nonprofits w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
Nonprofits w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 4,935 & 1,330 & 1,815 & 12,320 & 2,880 & 4,065\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with uncompensated care and CMI as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{7}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_uncompCMI_synth}Comparison to For-Profit Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Uncompensated Care} & \multicolumn{3}{c}{Case Mix Index} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Programs & 0.06$^{***}$ & 0.08$^{***}$ & 0.06$^{***}$ & 0 & 0.02$^{*}$ & 0\\
 & (0.01) & (0.01) & (0.01) & (0.01) & (0.01) & (0.01)\\
\textbf{Comparison Group:} &  &  &  &  &  & \\
In-Sample NFPs & $\checkmark$ &  &  & $\checkmark$ &  & \\
NFPs w/ MD &  & $\checkmark$ &  &  & $\checkmark$ & \\
\addlinespace
NFPs w/out MD &  &  & $\checkmark$ &  &  & $\checkmark$\\
 &  &  &  &  &  & \\
Observations & 4930 & 1330 & 1815 & 12320 & 2880 & 4065\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Results from Equation with uncompensated care and CMI as outcome variables.}\\
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{7}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}
